
\documentclass[11pt]{article}

\usepackage{pgfplots}
\usepackage{tikz}
\usepackage{amsmath}
\usepackage{amssymb}     % for mathbb
\usepackage{enumerate}
\usepackage{xfrac}
\usepackage{float}
\usepackage{hyperref}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{booktabs}    % for beautiful tables
\usepackage{siunitx}     % for si units
\usepackage{color}
\usepackage{titlesec}    % for header spacing

\usepackage[backend=bibtex,style=ieee]{biblatex}

% set margins
\addtolength{\oddsidemargin}{-.875in}
\addtolength{\evensidemargin}{-.875in}
\addtolength{\textwidth}{1.75in}
\addtolength{\topmargin}{-.875in}
\addtolength{\textheight}{1.75in}

\setlength{\parindent}{0cm}        % no paragraph indentations
\setlength{\parskip}{0.5em}        % small paragraph spacing

\titlespacing\section{0pt}{10pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{10pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\titlespacing\subsubsection{0pt}{10pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}

\DeclareMathOperator*{\argmax}{arg\,max}

\newcommand{\calcium}[0]{Ca\textsuperscript{2+}}
\newcommand{\todo}[1]{\textcolor{red}{#1}}
\providecommand{\tw}[1]{{\tw[TIM: #1]}}

\AtEveryBibitem{
\ifentrytype{inproceedings}{
    \clearlist{address}
    \clearlist{publisher}
    \clearname{editor}
    \clearlist{organization}
    \clearfield{url}  
    \clearfield{doi}  
    \clearfield{pages}  
    \clearlist{location}
 }{}
 }

\addbibresource{ref.bib}
\renewcommand*{\bibfont}{\footnotesize}

\begin{document}

\begin{center}
    {\LARGE Clustering of Neurons from Large-Scale Calcium Imaging Data}

    Stats 306b Project Proposal

    Mohammad Ebrahimi and Tim Wheeler

    Spring 2015
\end{center}

\section{Introduction}

Fluorescent imaging allows for the analysis of signalling behavior on a per-neuron basis in anesthetized and awake behaving animals. 
Existing methods monitor {\calcium} dynamics over a large region, but recently developed automated methods allow for isolating signals and associating them with particular neurons.
One proposed method leverages spatio-temporal sparseness in elevated [\calcium] levels to identify neuronal spikes and associate them with particular regions in the source frames.
The resulting work suffers from the presence of background structure such as blood vessels.
This project aims to apply unsupervised learning methods to identify classes of identified objects from one-photon {\calcium} imaging in the primary visual cortex (V1) of awake behaving mice to aid in the automatic unsupervised classification of neurons from background structures.

\section{Dataset}

This project will use an existing dataset obtained using one-photon {\calcium} imaging in the primary visual cortex of awake behaving mice performing a \num{30}-minutes go/nogo task.
Video recordings are available for three consecutive days of \num{30}-minute sessions each.
Data are presented as frame images associated with each of the extracted independent components (ICs).
Images are black and white frame averages that show the strength of each IC over the segmented field of view. 
Each IC indicates the flourscent signal of one independent object which may be a neuron, part of a blood vessel, or background noise.

The ICs are sampled at \num{6.7}\si{Hz}, totalling \num{1200} samples over each \num{30}-minute recording. 
Each recording contains a few thousand extracted objects, the idendity and quantity of which will vary between recordings.
The original raw videos are also available and could provide additional information.

\section{Approach}

Offline clustering methods will be used to identify relevant object classes from segmented image data and associated intracellular [\calcium] signals.
The resulting classes may provide crucial insight in distinguishing between neurons and background structure present in the extracted data.

\begin{table}[h]
    \centering
    \scriptsize
    \begin{tabular}{ccc}
        \toprule
        
        \begin{tabular}{l}
            candidate clustering methods \\
            \midrule
            Kernel $k$-means \\
            tree-structured vector quantisation \\
            agglomerative hierarchical clustering \\
            deep learning\\
            \\
        \end{tabular} & 

        \begin{tabular}{l}
            segmented image data over time \\
            \midrule
            principle components \\
            auto-encoded feature space \\
	    morphological features\\ 
	    dependency to surronding objects\\
            \\
        \end{tabular} & 

        \begin{tabular}{l}
            \calcium time histories \\
            \midrule
            frequency content \\
            mean peak amplitude \\
            mean peak width \\
            signal-to-noise ratio \\
            matched filtered data\\
        \end{tabular} \\

        \bottomrule
    \end{tabular}
\end{table}

\section{Measurement of Success}

Success of the project will be measured in the ability of a clustering method to correctly distinguish between neurons and background structure and identification of the key features used to make the distinction.
A subset of the training data is labelled, and can thus be used to compute a validation score.
Additional success metrics include the identification of subsets of neuron classes.

% \newpage

\printbibliography

\end{document}